\declareIM{j}{J}{2021-XX-YY}{Start/End of Night (with AuxTel)}{AT start/end night}

Executive Summary:

Exercise handoffs between day crew and night crew. Perform afternoon calibrations.
Perform observatory opening/closing. 
Requires definition of opening/closing procedures and appropriate observing conditions.
Also requires mechanism to get knowledge from night crew into Jira tickets which are then subsequently.
How do we use LOVE/EUI/notebooks to troubleshoot/resolve faults?

\textbf{Doesn't map to P6}

\subsection{Goals of IM}
\begin{itemize}
\item Have observing specialist run the AuxTel, including
  \begin{itemize}
  \item Perform nighttime hand off sequence
  \end{itemize}
\item Run afternoon calibrations, reduce them using \gls{OCPS}, run QA, and possibly certify for use
\item Test Camera Image Visualization Tool
  \begin{itemize}
  \item This is a camera deliverable and I'm completely unaware of it's status.
  \end{itemize}
\item Verify current environmental conditions against acceptable conditions (Where are these hosted?)
  \begin{itemize}
  \item Winds, seeing, humidity, windshake conditions (shutter/vent gate configurations), temperature
  \end{itemize}
\item Run opening script
  \begin{itemize}
  \item Functionality requires review to ensure component safety etc.
  \item When do we start observing?
  \end{itemize}
\item Perform several standard (spectroscopic) AuxTel visits
  \begin{itemize}
  \item Simulate a fault, have pre-derived written instructions to "reset" 
    \begin{itemize}
    \item Instructions must not include syntax!
      \begin{itemize}
      \item e.g. unwrap rotator, manually close vent gates 1-3, put down and push up mirror, home hexapod and re-position etc,
      \end{itemize}
    \end{itemize}
  \item Use logger to record important information
  \item Create Jira ticket(s)
  \item Run pre-derived commands
  \end{itemize}
\item Recover, Perform more visits
  \begin{itemize}
  \item Simulate weather event requiring closure of observatories
  \end{itemize}
\item Recover, perform more visits
\item Sun rising, Close observatory, publish night report
\item Perform daytime handoff, including the procedure to getting the JIRA tickets filtered and addressed accordingly
\end{itemize}

\subsection{Prerequisites}
\begin{itemize}
\item AuxTel system fully functional
\item LOVE screens should be operational for mount/dome/mirrors(?)
\item RLS system with fault reporting
\item EAS
\end{itemize}
