\declareIM{pc}{3a}{2021-05-31}{Rubin AuxTel Standard Star Campaign}{AT Scripted}
\completeIM{\thisIM}{2021-06}

Executive Summary:

Demonstrates ability to take and reduce AuxTel data

\textbf{No direct mapping to P6 activity, indirect mappings are below}

\subsection{Goals of IM}
\begin{itemize}
\item Automated generation and availability of AuxTel master calibrations in Chile (cf. \IM{b}) - \textbf{\JIRA{SUMMIT}{2989}{Atmospheric Calibration Products Pipeline Testing}}
\item Annotate exposures using \gls{RLS}
\item Take data in a standard star field, including interactive re-centering \textbf{}
\item Run AuxTel data analysis package in Chile and NCSA, triggered by \gls{OCPS} \textbf{Partial mapping to \JIRA{SUMMIT}{2987}{Calibration Telescope Instrumental Signature Removal Testing \& Verification} and \JIRA{SUMMIT}{2871}{Aux. Tel. DAQ + DMS Interface Testing}}
\begin{itemize}
\item Display results to operators % (may require publishing to EFD?)
\end{itemize}
\end{itemize}

\subsection{Prerequisites}
\begin{itemize}
	\item{\IM{b} Completed}
	\item{AuxTel and LATISS functional and ready to track a target. Rough focus should be achieved.}
	\item{Available staff for night time operations}
	\item{User commenting in \gls{RLS} available}
\end{itemize}

\subsection{Procedure}
The following procedure is to be executed by an observing specialist.
\begin{enumerate}
	\item Using Nublado, slew to $\sim$~60 degree elevation target and start tracking
	\item Using Nublado, measure the focus offset using the \href{https://github.com/lsst-ts/ts_externalscripts/blob/develop/python/lsst/ts/externalscripts/auxtel/latiss_cwfs_align.py}{CWFS focus script}, but launched from the notebook.
	\item Annotate results using the \gls{RLS}
	\item Apply the focus offset using the ATAOS, record the applied offset in the \gls{RLS}
	\item Manually take a single OBJECT image:
	\begin{enumerate}
		\item Verify functionality of the \gls{LOVE} interface, including instrument setup and applied focus offset(s).
		\item Perform basic \gls{ISR} on the image using DM code
		\item Display the image after running \gls{ISR}
	\end{enumerate}	
	\item Using the standard visit script launched from a notebook, slew to new target and perform automated acquisition only, script must have user verify offset prior to motion.
	\item Perform the standard data taking sequence using the standard visit script
	\item Perform a single image with the instrument in its standard spectral mode
	\item Perform a custom sequence using at least two items in the grating wheel and two in the filter wheel, all with different exposure times
	\begin{enumerate}
		\item Verify functionality of the \gls{LOVE} interface, including filter/grating changes/shutter movement, focus/pointing offsets
		\item Display the \gls{ISR} processed images as they are available
	\end{enumerate}	
	\item Manually and off-line:
		\begin{enumerate}
			\item Perform standard observations of 3 targets spanning the elevation range sequentially			\item Display extracted atmospheric parameters for each target % HOW?
		\end{enumerate}
\end{enumerate}
