\documentclass[SE,authoryear,toc]{lsstdoc}
% lsstdoc documentation: https://lsst-texmf.lsst.io/lsstdoc.html
\input{meta}

% Package imports go here.
\usepackage{xspace}

% Local commands go here.
\renewcommand{\c}{\textit{c.}\xspace}
\newcommand{\cf}{\textit{cf.}\xspace}

\newcommand{\IM}[1]{\hyperref[IM:#1]{\color{blue}IM$_{\text{\csname nameIM#1\endcsname}}$}}
\newcommand{\declareIM}[4]{%
  % \declareIM{label}{short name}{date}{title}
  % e.g.
  %    \declareIM{b}{B}{2021-XX-YY}{ComCam Image Capture and Archive}
  % where you refer to the IM as \IM{b} and it appears as IM_B
  %
  \section{IM\texorpdfstring{$_{\text{#2}}$}{#2}: #4 (#3)}%
  \label{IM:#1}%
  \expandafter\newcommand\csname nameIM#1\endcsname{#2}%
}


%If you want glossaries
\makeglossaries
\input{aglossary.tex}
\glsunsetall  % never expand acronyms
\iftrue\else % colour rather than box acronyms
   \AtBeginDocument{\hypersetup{pdfborder={0 0 0}}}
   \renewcommand*{\glstextformat}[1]{\textcolor{red}{#1}}
\fi

\title{Integration Milestones}

% Optional subtitle
% \setDocSubtitle{A subtitle}

\author{%
Robert Lupton
}

\setDocRef{SITCOMTN-006}
\setDocUpstreamLocation{\url{https://github.com/lsst-sitcom/sitcomtn-006}}

\date{\vcsDate}

% Optional: name of the document's curator
% \setDocCurator{The Curator of this Document}

\setDocAbstract{%
A proposal for ways to work on predominantly software subsystem commissioning,  building on the Rubin AuxTel (n\'ee auxTel) experience
}

% Change history defined here.
% Order: oldest first.
% Fields: VERSION, DATE, DESCRIPTION, OWNER NAME.
% See LPM-51 for version number policy.
\setDocChangeRecord{%
  \addtohist{1}{YYYY-MM-DD}{Unreleased.}{Robert Lupton}
}

\begin{document}

\maketitle

\section{Introduction}

The Rubin construction project is composed of three main subsystems: DM, Camera, and T\&S.\footnote{
  And also EPO, but this is probably not relevant here.}
but in operations there is only one survey.  The task of merging the projects is not easy, especially
when some of the interfaces are underspecified, or turn out to need modification based on experience.
This is primarily
a problem for the software --- the hardware interfaces, specified in mm and screw threads, are generally
well defined.

Once we accept that the only way to complete the integration of the subsystems is to actually integrate them,
while expecting that the interfaces and requirements will evolve, we recognise that our
situation is analogous to the
way that software development has moved from waterfall to agile development models.

This technote proposes that we introduce the concept of an \gls{IM} which defines
a specified set of functionalities that are available to the Rubin project.
This is slightly different from \gls{DM}'s
current \gls{OR} concept which tests the state of DM systems at a certain time rather than guaranteeing
continued cross-subsystem functionality.  I envisage that an \gls{IM} would be followed by an \gls{OR} to test
the deliverable, and to carry out an internal \gls{ORR} for the functionality delivered by the \gls{IM}.

\newcommand{\inputIM}[1]{\vfil\eject\input{#1}}
\inputIM{IMa}
\inputIM{IMb}
\inputIM{IMc}
\inputIM{IMd}
\inputIM{IMe}
\inputIM{IMf}
\inputIM{IMg}
\inputIM{IMh}
\inputIM{IMi}
\inputIM{IMj}
\inputIM{IMk}
\inputIM{IMbacklog}

\appendix
% Include all the relevant bib files.
% https://lsst-texmf.lsst.io/lsstdoc.html#bibliographies
\section{References} \label{sec:bib}
\renewcommand{\refname}{} % Suppress default Bibliography section
\bibliography{local,lsst,lsst-dm,refs_ads,refs,books}

% Make sure lsst-texmf/bin/generateAcronyms.py is in your path
%\section{Acronyms} \label{sec:acronyms}
%\input{acronyms.tex}
% If you want glossary uncomment below -- comment out the two lines above
\printglossaries

\end{document}
